Geometric Control for Autonomous Landing on Asteroids

### 2017-08-07 manuscript.tex
Add camera parameters

Images of asteroid Itokawa are simulated using Blender, a free and open-source computer graphics software program~\cite{blenderfoundation1995--2017}.
Blender is primarily used by the animation and computer modeling fields to create computer generated images, videos and animations for films and video games. 
Blender offers the capability of accurately modelling the various effects of camera, lighting, and surface properties of a scene using the \texttt{cycles} path-tracing rendering engine.
A unique feature is the ability to compile the Blender rendering software as a python module.
This allows one to use the capabilities of Blender through a Python API in personal scripts and functions programmatically, rather than through a desktop based graphical interface.
A camera is simulated within blender with the following parameters, which are chosen to emulate the primary sensor of the NEAR spacecraft~\cite{hawkins1997}.
\begin{table}
    \centering
\begin{tabular}{llr}  
\toprule
Parameter & Description &  Value\\
\midrule
FOV & horizontal field of view & \SI{2.25}{\degree}       \\
    &    vertical field of view  & \SI{2.90}{\degree}\\
Image Size & horizontal & \SI{537}{\px}\\
           & vertical & \SI{244}{\px}\\
\(f\)& focal length & \SI{167.35}{\milli\meter}\\
\bottomrule
\end{tabular}
\caption{Camera parameters used in simulation}
\end{table}

>>>>

Images of asteroid Itokawa are simulated using Blender, a free and open-source computer graphics software program~\cite{blenderfoundation1995--2017}.
Blender is primarily used by the animation and computer modeling fields to create computer generated images, videos and animations for films and video games. 
Blender offers the capability of accurately modelling the various effects of camera, lighting, and surface properties of a scene using the \texttt{cycles} path-tracing rendering engine.
A unique feature is the ability to compile the Blender rendering software as a python module.
This allows one to use the capabilities of Blender through a Python API in personal scripts and functions programmatically, rather than through a desktop based graphical interface.
A camera is simulated within blender with the parameters shown in~\cref{tab:camera_parameters}, which are chosen to emulate the primary sensor of the NEAR spacecraft~\cite{hawkins1997}.
\begin{table}
    \centering
\begin{tabular}{llr}  
\toprule
Parameter & Description &  Value\\
\midrule
FOV & horizontal field of view & \SI{2.25}{\degree}       \\
    &    vertical field of view  & \SI{2.90}{\degree}\\
Image Size & horizontal & \SI{537}{\px}\\
           & vertical & \SI{244}{\px}\\
\(f\)& focal length & \SI{167.35}{\milli\meter}\\
\bottomrule
\end{tabular}
\caption{Camera parameters used in simulation~\label{tab:camera_parameters}}
\end{table}
